Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-13 programlogic.tex
+

  \{P \ast \mathcal{I}\textsf{ASpace}\ast r_d \mapsto_{r}  \textsf{rvd} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{v} \}_{\textsf{rtv}}

@@

  \{P \ast \mathcal{I}\textsf{ASpace}\ast r_s \mapsto_{r}\{q\}  \textsf{rvs}  \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{v} \}_{\textsf{rtv}}\;\overline{ is}  

@@

  \{P \ast \mathcal{I}\textsf{ASpace}\ast r_s \mapsto_{r}\{q\}  \textsf{rvs}   \ast r_a \mapsto_{r}\{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{rvs} \}_{\textsf{rtv}}

@@

\caption{Reasoning Rules for Selected \textsf{AMD64} Instructions}

>>>>

  \{P \ast \mathcal{I}\textsf{ASpace}\ast r_d \mapsto_{r}  \textsf{rvd} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{v} \}_{\textsf{rtv}}

@@

  \{P \ast \mathcal{I}\textsf{ASpace}\ast r_s \mapsto_{r}\{q\}  \textsf{rvs}  \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{v} \}_{\textsf{rtv}}\;\overline{ is}  

@@

  \{P \ast \mathcal{I}\textsf{ASpace}\ast r_s \mapsto_{r}\{q\}  \textsf{rvs}   \ast r_a \mapsto_{r}\{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{rvs} \}_{\textsf{rtv}}

@@

\caption{Reasoning Rules for Selected \textsf{AMD64} Instructions under}
